---
title: "Essays in -"
author: "Luisa Carrer"
date: "26-10-2023"
output:
  xaringan::moon_reader:
   css: [default, metropolis, metropolis-fonts]

---

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE,
                      echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

```{r}
library(tidyverse)
```

```{r}
penguins <- read_csv("https://raw.githubusercontent.com/rfortherestofus/r-without-statistics/main/data/penguins-2008.csv")
```


# Introduction

We are writing a report about the **Palmer Penguins**. These penguins are *really* amazing. There are three species:

- Chapter 1: *Learning about in-group or out-group facts and the role of the presenter*
    - What is the impact on mipserpception and learning of racial identity congruence?
- Chapter 2: *Identity Characteristics and Judgments on Research(er) Quality*
    - What is the impact of idernity of research content and author on how they are perceived?
- Chapter 3: *Gender-segregated events: soccer and gender norms*
    - What is the impact of idernity of research content and author on how they are perceived?


---

[comment]: # (CHAPTER 1)

class: inverse, right, middle
# Learning about in-group or out-group facts and the role of the presenter

---

.panelset[
.panel[.panel-name[Congruence 1]

```r
hist(runif(100))
```
]

.panel[.panel-name[Congruence 2]

Take a look at the R code in that other panel.
]
]



---

[comment]: # (CHAPTER 2)

class: inverse, right, middle
# Identity Characteristics and Judgments on Research(er) Quality

---

---

[comment]: # (CHAPTER 3)
class: inverse, right, middle
# Gender-segregated events: soccer and gender norms

---

#Introduction

- Role of gender norms in perpetuating gender gaps
-


- Male dominated sport in terms of fanship base in certain countries

-  I study how individuals’ gender norms can evolve in their formative years when they are exposed to an environment where these gendered norms become more salient.

- Short-term effects
 - Immediate (one-year) effects of teenage pupils on school choices
- Long-term effects
 - Long-term effects on gender norms


---

#Data

### Soccer
- Italian football I and II division
- Scraped from various online sources
- Constructed 1945-2018 final results

### School from MIUR
- High school-level data from 2015-2019
- New entry

### Value
- European Value Survey data at NUTS3


